Edge sign prediction in general graphs and Correlation Clustering

### 2017-12-12 conclusion/main.tex
be smoother in the future work conclusion

Unfortunately, we did not study this problem further in this thesis. Indeed, getting data and
testing algorithms usually require an industrial partner.\footnote{See for
instance~\autocites{Andrews2015}{Kille2015}{Krzywicki2015}{Xia2015}{Alanazi}}

@@

As we mentioned already in \autoref{sec:troll_related} and \autoref{sec:edge_related}, a recent and
promising trend regarding learning in graph is node embedding. In addition to the references cited
earlier, this also witnessed by recent works on embedding attributed nodes, either in signed
graphs~\autocites{SignedFS17}{attributedSNE17}{SHINE18} or in general
graphs~\autocites{Liao2017}{AANE17}{DynamicEmbedding17}. At first sight, those methods seem
radically different from traditional graph methods. However, just like word embedding methods have
been linked to matrix
factorization~\autocites{WordEmbeddingAsFactorization14}{Hellinger14}{AroraRandWalk16}, so have been
popular and successful node embedding methods~\autocite{embeddingAsFactorization18}. These methods
are the simple ones that do not consider node attributes and multiple types of edges, such as
DeepWalk~\autocite{DeepWalk14}, LINE~\autocite{LINE15} and node2vec~\autocite{node2vec16}. For
instance, \textcite{embeddingAsFactorization18} show that the node embedding of DeepWalk on the
weighted graph $G$ are approximately the left singular vectors of the following matrix:
\begin{equation}
  \label{eq:deepwalk}
  \log \left( vol(G) \left( \frac{1}{T} \sum_{r=1}^T (D^{-1}A)^r\right) D^{-1} \right) - \log b
\end{equation}
where $vol(G)$ is the sum of all weighted degrees, $T$ is the context window size, $D$ is the
diagonal matrix of degrees, $A$ is the adjacency matrix of the graph and $r$ is the number of
negative samples in skip-gram. There are several ways such findings could be used in our context:
\begin{itemize}

>>>>

As in any worthy machine learning endeavor, reliably evaluating and comparing approaches require
large amount of real data. This is particularly true in such an applied setting, but the most
realistic evaluation is to perform A/B testing on a live system with enough traffic to give some
statistical significance. This explains why most previous studies rely on the cooperation of
industrial partners~\autocites{Andrews2015}{Kille2015}{Krzywicki2015}{Xia2015}{Alanazi}. Thus, this
is also something we would like to do in the future.

@@

A fundamental question underlying many machine learning approaches is the representation of data.
When extracting information from the real world, we are usually given some freedom in how to present
it to learning algorithms. Ideally, we would like to use the representation providing the best
performance in the learning task. One solution is to ask expert domains to craft relevant features
based on their prior knowledge. While this has achieved successes, it is not scalable to the present
day situation, where the deluge of available data has prompted the use of machine learning in every
corner of the society. An alluring alternative to expert knowledge is to learn the data
representation itself, guided by the task.

As an illustration in the context of this thesis, we assume that data was organized as a graph,
where nodes were possibly associated with a feature vector. However, there might an different
representation of those nodes that would better suit our needs. Indeed,
we mentioned already in \autoref{sec:troll_related} and \autoref{sec:edge_related} that a recent and
promising trend regarding learning in graph is node embedding. In addition to the references cited
earlier, this also witnessed by recent works on embedding attributed nodes, either in signed
graphs~\autocites{SignedFS17}{attributedSNE17}{SHINE18} or in general
graphs~\autocites{Liao2017}{AANE17}{DynamicEmbedding17}. At first sight, those methods seem
radically different from traditional graph methods. However, just like word embedding methods have
been linked to matrix
factorization~\autocites{WordEmbeddingAsFactorization14}{Hellinger14}{AroraRandWalk16}, so have been
popular and successful node embedding methods~\autocite{embeddingAsFactorization18}. These methods
are the simple ones that do not consider node attributes and multiple types of edges, such as
DeepWalk~\autocite{DeepWalk14}, LINE~\autocite{LINE15} and node2vec~\autocite{node2vec16}. For
instance, \textcite{embeddingAsFactorization18} show that the node embedding of DeepWalk on the
weighted graph $G$ are approximately the left singular vectors of the following matrix:
\begin{equation}
  \label{eq:deepwalk}
  \log \left( vol(G) \left( \frac{1}{T} \sum_{r=1}^T (D^{-1}A)^r\right) D^{-1} \right) - \log b
\end{equation}
where $vol(G)$ is the sum of all weighted degrees, $T$ is the context window size, $D$ is the
diagonal matrix of degrees, $A$ is the adjacency matrix of the graph and $r$ is the number of
negative samples in skip-gram. There are several ways such findings could be used in our context:
\begin{itemize}
